conmat: generate synthetic contact matrices for a given age-stratified population

### 2024-06-13 paper/paper.Rmd
Updated paper

Epidemiologists and public policy makers need to understand the spread of infectious diseases in a population. Knowing which groups are most vulnerable, and how disease spread will unfold facilitates public health decision-making. Diseases like influenza and coronavirus spread via human-to-human, "social contact".  If we can measure the amount of social contact, we can use this to understand how diseases spread.

We can measure social contact through social contact surveys, where people  describe the number and type of social contact they have. These surveys provide an empirical estimate of the number of social contacts from one age group to another, as well as the setting of contact. For example, we might learn from a contact survey that homes have higher contact with 25-50 year olds and with 0-15 year olds, whereas workplaces might have high contact within 25-60 year olds.

>>>>

Epidemiologists and public policy makers need to understand the dynamics of infectious disease transmission in a population. Identifying vulnerable groups and predicting disease transmission dynamics are essential for informed public health decision-making. Infectious diseases such as influenza and coronavirus spread through human-to-human interactions, or in other words, "social contact". Quantifying social contact and its patterns can provide critical insights into how diseases spread.

We can measure social contact through social contact surveys, where people  describe the number and type of social contact they have. These surveys provide an empirical estimate of the number of social contacts from one age group to another and the setting of contact. For example, we might learn from a contact survey that homes have higher contact between 25-50 year olds and 0-15 year olds, whereas workplaces might have high contact within 25-60 year olds.
